\begin{preface}{Chapter Summary}
  \textbf{Chapter 1: Introduction to the Topic}
  \\
  Introduction to the overview, significance, objectives, and limitations of the thesis topic.
  \\
  \\
  \textbf{Chapter 2: Foundation Knowledge}
  \\
  Introduction to fundamental theoretical knowledge, new technologies applied including programming languages, frameworks, libraries, third-party services,.... that used in building and deploying the system.
  \\
  \\
  \textbf{Chapter 3: System Analysis}
  \\
  This chapter presents system survey information, specifications, and analysis of potential features. It defines the actors and their roles, and presents use case diagrams illustrating the system's interactions.
  \\
  \\
  \textbf{Chapter 4: System Design}
  \\
  This chapter covers the database design, overall system architecture. It describes the design methodology and approaches used in developing the system.
  \\
  \\
  \textbf{Chapter 5: System Implementation}
  \\
  This chapter introduces the libraries used in the system, implementation methods, and execution flow through the description of the system interface.
  \\
  \\
  \textbf{Chapter 6: Testing and System Evaluation}
  \\
  This chapter details the testing methodologies, and evaluation of system performance. It explores ways to improve system efficiency and reliability.
  \\
  \\
  \textbf{Chapter 7: Summary, Evaluation and Development Direction}
  \\
  This chapter summarizes the achievements throughout the project implementation, evaluates the system through its strengths and weaknesses, and provides necessary development directions for the system in the future.
  \end{preface}