\chapter{Summary, Evaluation and Development Direction}
\section{Achieved outcomes}
After the completion of this project, we have successfully achieved the following outcomes:
\begin{itemize}
  \item Conducted comprehensive research and analysis of logistics business operations to develop FreightFlex, a user-friendly and flexible web application.
  \item Applied advanced front-end programming techniques to create a modern, intuitive, and aesthetically pleasing user interface.
  \item Implemented back-end programming methodologies to establish a high-performance architecture with stable connectivity.
  \item Developed a system with comprehensive features tailored to fulfill the requirements of freight forwarding service users.
  \item Enhanced team expertise in programming, collaborative work practices, and project management strategies throughout the development process.
\end{itemize}
\section{System Evaluation}
\noindent \textbf{Strengths}
\begin{itemize}
  \item The system is easy to use and flexible, allowing users to customize their experience.
  \item The system is built on a modern technology stack, ensuring high performance and stability.
  \item The system is designed with security in mind, ensuring that user data is protected.
  \item The system is designed to be scalable, allowing for future growth and expansion.
  \item The system is designed to be modular, allowing for easy integration with other systems and services.
\end{itemize}
\noindent \textbf{Weaknesses}
\begin{itemize}
  \item The system may require additional testing and optimization to ensure optimal performance.
  \item The system may require additional documentation and training materials to help users understand how to use it effectively.
  \item Business logic may need to be adjusted to meet the specific needs of different users.
  \item The system may took time to load on slower internet connections.
\end{itemize}
\section{Future Development Direction}
After developing the system, we have identified several areas for future development. These include:
\begin{itemize}
  \item Developing additional freight rate type to meet all user needs.
  \item Implementing additional features to enhance the user experience, such as a mobile app or additional reporting capabilities.
  \item Implementing Microservices architecture to improve system performance and scalability.
  \item Implementing additional security measures to protect user data and ensure compliance with industry standards.
  \item Integrate chat bots or AI-driven customer support to enhance user assistance and engagement.
  \item Implementing features related to data tracking and analytics to provide users with insights into their freight operations.
  \item Implementing features related to payments to enhance user convenience and flexibility.
\end{itemize}